Supplemental Material for ``Assessing United States county-level exposure for research on tropical cyclones and human health"

### 2020-09-03 ehp_revision/response_to_reviewers.Rmd

\begin{shaded}
\textbf{R1 Comment 3:}
In non-health fields, a county's inclusion in a FEMA major disaster declaration
or eligibility for public/individual assistance (all of which are somewhat
reflective of level of damage) is sometimes used as an "exposure" proxy. Have
you considered if/how your exposure assessments relate to inclusion in a FEMA
disaster declaration? In other words, does exposure to any of the hazards align
with the level of damage required for a county to be considered a "disaster
area" and/or worthy of federal assistance by current federal policy? Does this
matter?
\end{shaded}

**Response:**

This is a great question, and we are aware of a number of studies on the
societal impacts of tropical cyclones that have used FEMA disaster declarations
to assess county-level exposure to tropical cyclones.

There are two elements that are important related to this question. First, many
of the health impacts of tropical cyclones will likely come through indirect
pathways, including through damage to property and infrastructure. Ultimately,
it would be useful to have large-scale databases of these secondary exposure
pathways to use for more complex studies of the pathways between the physical
hazards of these storms and how they affect human health. In this sense,
something like the FEMA declarations could be considered not as a proxy for
assessing exposure to physical hazards, but rather as a proxy of damage caused
by the storm, and so a measurement informative for one of these indirect
pathways from physical hazards of the storm to health impacts, through something
like a mediation analysis. We have added text to the manuscript on this point:

...

In terms of using FEMA declarations as a source for this, however, there are 
some limitations. These declarations are on average tied to the amount of 
damage and other impacts experienced following a storm, but there are a number
of other considerations that drive whether a disaster is declared or not. 
These contributing factors could vary by location (especially from one state
to another) and also over time, especially over the long period we've included
for our other data. Given that, these may not be the best data source to use
to try to capture estimates of the damage or impacts to a community in a multi-year, 
multi-site dataset like the one we present.

FEMA's disaster declarations are issued to provide assistance, based on damage
assessment, to individuals or the entire public in certain locations where
catastrophes overwhelm the state or local government [@mccarthy2014fema], and
any use of them for exposure assessment is secondary. Due to the political
nature of disaster declaration process, these declarations are often subject to
many political and economic factors [@mccarthy2014fema; @logue1981research]. One
epidemiological study specifically focused on exposure assessment for tropical
cyclone epidemiology and compared use of FEMA declarations with other methods of
exposure assessment, including one based directly on the storm hazard of wind
[@grabich2015measuring]. They found that exposure assessment based on FEMA
declarations tended to overassign counties to be "exposed," resulting in false
positives [@grabich2015measuring]. A further concern is that, given the
political and economic nature of these declarations, there is likely variation
across time and geography in the likelihood of a given exposure resulting in a
disaster declaration. This is particularly worrisome for a study that seeks to
explore risk across multiple years and affected communities.

Other sources of data may be better suited to use as a marker of damage to
assess that pathway of indirect health impacts from a tropical cyclone. For
example, data on storm impacts, including property damage or insurance claims
data, are sometimes available through storm databases or publications (e.g.,
NOAA's Storm Events data, *Monthly Weather Review*). While such data could
potentially be used to create an exposure metric, tropical storm damage data
requires some normalization, to incorporate both changes in dollar value over
time and also changes in development in at-risk areas, to be comparable over
extended time periods [@Pielke1998].

However, evidence from prior tropical cyclone epidemiology that doing so is
problematic and should be avoided [@grabich2015measuring].

@@

> **Text in revised manuscript:**
"While other approaches have been developed to incorporate storm
hazards, particularly wind, into exposure assessment (e.g., Grabich et al.
2015a; Zandbergen 2009; Czajkowski et al. 2011), there is not yet a standard
approach. When different studies use different datasets or storm hazards
when assessing storm exposure, it becomes difficult to compare and aggregate
findings."

\begin{shaded}
\textbf{R1 Comment 6:}
This is not a comment on the paper, but the authors may also want to consider
publishing their work in DesignSafe, which is "the web-based research platform
of the NHERI  [NSF-Funded Natural Hazards Engineering Research Infrastructure]
Network that provides the computational tools needed to manage, analyze, and
understand critical data for natural hazards research." It is the data
repository widely used by interdisciplinary hazards and disaster researchers.
\end{shaded}

**Response:**

It turns out that it should already be accessible to use on the DesignSafe
platform, because we have shared the data as an R package.

@@

We have added estimates of these correlations specifically for
high-precipitation events in a new table in the Supplemental Material (Table S1,
reproduced as Table \@ref(tab:highprecipcorr) of this response document).

\input{tables/precip_high_corr.tex}

In several cases, the correlation was much weaker when limiting analysis to
these severe rainfall events. For example, in Miami-Dade County, FL, the
Spearman correlation coefficient was 0.94 for all 64 tropical cyclones that came
near the county over the analysis period, while it was only 0.49 among the 18
storms with cumulative precipitation of 75 mm or more. There was a similar
reduction in Mobile County, AL. However, for some counties, the correlation
remained high (e.g., Harris County, TX; Orleans Parish, LA), although in all
cases there are small numbers of extreme precipitation events (5--20 across
these sample counties), and so there is likely substantial random variation in
these correlation estimates, since they are based on small numbers of 
observations.

We have added text to mention this point and to direct readers to the added
supplemental table:

> **Text in revised manuscript (relevant addition in bold):**
"The rainfall data are generally well-correlated with ground-based
observations, but may sometimes underestimate very high rainfall values (Figure
2), **and in some counties the correlation was substantially lower when 
considering only tropical cyclones with cumulative local rainfall of 75 mm
or more (Supplemental Table 1)**."

@@

\begin{shaded}
\textbf{R2 Comment 5:}
Line 602: This is not a new finding, but how much misclassified would be a good
question to answer.

\textit{Line 600--602 from original manuscript:}

\begin{quotation}
\noindent
\textit{"Based on our results, the use of a distance-based metric to assess
exposure to any of these hazards, or the use of measurements from one hazard as
a proxy for exposure to any of the other hazards considered, would often
introduce exposure misclassification."}
\end{quotation}
\end{shaded}

Figure 7 of the main text is meant to help illustrate the potential for 
exposure misclassification, including when using a distance-based metric as
a proxy. We selected to use the Jaccard index because we are using data for 
counties at a large spatial scale. For any storm, there will be large parts of
our study area that are clearly unaffected, because they are so far from the 
storm. If we measured misclassification using a metric that includes these
counties in the denominator, it would be overly optimistic, and wouldn't help
to pinpoint the potential for disagreement in areas nearer the storm path.

However, one downside of this metric is that it does not help readers understand
the direction that disagreement is going. For example, it does not provide 
information about how many counties were classified as "exposed" based on a 
distance proxy but "unexposed" by a hazard-based proxy. This could be useful in 
interpreting our results in Figure 7 of the main table.

We have added four new tables in the Supplemental Material, one for each of the 
hazard-based metrics we considered. We have reproduced these tables in this response
document as Tables [x]--[x] Each breaks down agreement and disagreement
between the distance-based proxy metric and that hazard-based metric within several
storms in our study period, focusing on storms with at least 250 counties exposed
by at least one of the metrics considered. All of these storms are included in 
Figure 7.

\input{tables/wind_misclass.tex}

\input{tables/rain_misclass.tex}

\input{tables/flood_misclass.tex}

\input{tables/tornado_misclass.tex}

These tables allow readers both to investigate general patterns in disagreement
and exposure misclassification across these storms and also to see cases of unusual 
storms. For example, for most storms, disagreement between the distance proxy 
metric and the wind-based metric resulted mainly from mis-classification of 
counties as exposed based on distance while they did not experience gale-force winds.
However, there were a few storms, like Hurricane Bertha in 1996, where the 
inverse was the case, and a distance-based metric would have missed a large number
of counties that experienced gale-force winds from the storm (misclassified them
as unexposed), but not misclassified many counties as exposed when they in fact
did not experience winds at this level.

We have added a reference to these new tables in the main text of the manuscript:

> **Text in the revised manuscript (relevant addition in bold):** 
"We drew similar conclusions when we investigated all 46 tropical cyclones
between 1996 and 2011 (when data for all five metrics were available) for which
100 or more counties were exposed based on at least one metric (Figure 7;
**Tables S[x]--S[x] provide the underlying numbers for the most extensive of
these, the storms for which 250 of more counties were exposed based on at least
one metric)**."

> **Text in the revised manuscript (relevant addition in bold):**
"Based on our results, the use of a distance-based metric to assess exposure to
any of these hazards, or the use of measurements from one hazard as a proxy for
exposure to any of the other hazards considered, would often introduce exposure
misclassification **(Tables S[x]--S[x])**."

@@

\begin{shaded}
\textbf{R3 Comment 3:}
Several of the exposures are calculated for the population mean center of each
county. From the reference list, it looks like the authors consistently used
population centers from 2010 throughout the years included in the dataset/R
package. If so, I suggest clarifying this in the text. 
\end{shaded}

**Response:**

This is correct---the population centers from the US 2010 Decennial Census were 
used throughout. We have added text to the manuscript to clarify this:

> **Text in revised manuscript (relevant addition in bold):**
"At each 15-min interval, we measured the distance between the storm's
center and each county's population mean center, **as of the 2010 US Decennial
Census** (US Census Bureau 2020)."

### 2020-09-03 ehp_revision/tables/rain_misclass.tex
Work some more on response

% latex table generated in R 4.0.2 by xtable 1.8-4 package
% Tue Sep  1 17:11:55 2020
\begin{table}[ht]
\centering
\caption{Caption. Limited to storms with at least 200 counties assessed as exposed based on at least one exposure metric considered in this study. Numbers are out of 2,396 counties in the study area (states in the eastern half of the US). Exposure assessment is based on the thresholds given in Table 1 of the main text. The Jaccard index shown in Figure [x] of the main text is based on numbers in the second through fourth columns (the value in the second column divide by the sum of numbers in the second through fourth columns.  Storms are ordered based on the number of counties exposed to at least one of these two exposure metrics.).} 
\begin{tabular}{cp{3cm}p{3cm}p{3cm}p{3cm}}
  \toprule
Storm & Classified as exposed based on both distance metric and rain metric & Classified as exposed based on distance metric but unexposed by rain metric & Classified as exposed based on rain metric but unexposed by distance metric & Classified as unexposed based on both distance metric and rain metric \\ 
  \midrule
Frances-2004 & 207 & 114 & 257 & 1818 \\ 
  Ivan-2004 & 124 & 160 & 288 & 1824 \\ 
  Isidore-2002 & 134 & 134 & 186 & 1942 \\ 
  Ike-2008 & 113 & 120 & 213 & 1950 \\ 
  Dennis-2005 &  48 & 244 & 124 & 1980 \\ 
  Fay-2008 &  72 & 180 & 163 & 1981 \\ 
  Jeanne-2004 & 144 & 153 & 113 & 1986 \\ 
  Lee-2011 & 106 &  38 & 230 & 2022 \\ 
  Gustav-2008 & 126 & 108 & 137 & 2025 \\ 
  Allison-2001 & 106 & 181 &  67 & 2042 \\ 
  Bill-2003 & 110 & 120 & 117 & 2049 \\ 
  Cindy-2005 &  78 & 243 &  11 & 2064 \\ 
  Floyd-1999 & 129 &  10 & 170 & 2087 \\ 
  Katrina-2005 & 195 &  46 &  58 & 2097 \\ 
  Danny-1997 &  82 & 147 &  54 & 2113 \\ 
  Rita-2005 &  64 & 101 & 103 & 2128 \\ 
  Gordon-2000 &   5 & 250 &   7 & 2134 \\ 
  Arlene-2005 &  39 & 197 &  23 & 2137 \\ 
  Dennis-1999 &  90 & 110 &  56 & 2140 \\ 
  Ernesto-2006 & 124 &  68 &  63 & 2141 \\ 
  Irene-2011 & 119 &   1 & 106 & 2170 \\ 
  Hanna-2008 & 100 &  92 &  33 & 2171 \\ 
  Hermine-2010 &  44 &  79 & 102 & 2171 \\ 
  Fran-1996 &  89 &  62 &  73 & 2172 \\ 
  Earl-1998 &  72 &  97 &  38 & 2189 \\ 
  Bertha-1996 & 103 &  80 &  20 & 2193 \\ 
  Helene-2000 &  28 & 164 &  11 & 2193 \\ 
  Frances-1998 &  27 &  35 & 139 & 2195 \\ 
  Josephine-1996 &  94 &  29 &  77 & 2196 \\ 
  Bonnie-2004 &  56 &  53 &  56 & 2231 \\ 
  Isabel-2003 &  88 &  59 &  17 & 2232 \\ 
   \bottomrule
\end{tabular}
\end{table}

>>>>

% latex table generated in R 4.0.2 by xtable 1.8-4 package
% Thu Sep  3 12:19:54 2020
\begin{table}[ht]
\centering
\caption{Caption. Limited to storms with at least 250 counties assessed as exposed based on at least one exposure metric considered in this study. Numbers are out of 2,396 counties in the study area (states in the eastern half of the US). Exposure assessment is based on the thresholds given in Table 1 of the main text. The Jaccard index shown in Figure [x] of the main text is based on numbers in the second through fourth columns (the value in the second column divide by the sum of numbers in the second through fourth columns.  Storms are ordered based on the number of counties exposed to at least one of these two exposure metrics.).} 
\begin{tabular}{cp{3cm}p{3cm}p{3cm}p{3cm}}
  \toprule
Storm & Exposed for both distance metric and rain metric & Exposed for distance metric but unexposed for rain metric & Exposed for rain metric but unexposed for distance metric & Unexposed for both distance metric and rain metric \\ 
  \midrule
Frances (2004) & 207 & 114 & 257 & 1,818 \\ 
  Ivan (2004) & 124 & 160 & 288 & 1,824 \\ 
  Isidore (2002) & 134 & 134 & 186 & 1,942 \\ 
  Ike (2008) & 113 & 120 & 213 & 1,950 \\ 
  Dennis (2005) & 48 & 244 & 124 & 1,980 \\ 
  Fay (2008) & 72 & 180 & 163 & 1,981 \\ 
  Jeanne (2004) & 144 & 153 & 113 & 1,986 \\ 
  Lee (2011) & 106 & 38 & 230 & 2,022 \\ 
  Gustav (2008) & 126 & 108 & 137 & 2,025 \\ 
  Allison (2001) & 106 & 181 & 67 & 2,042 \\ 
  Bill (2003) & 110 & 120 & 117 & 2,049 \\ 
  Cindy (2005) & 78 & 243 & 11 & 2,064 \\ 
  Floyd (1999) & 129 & 10 & 170 & 2,087 \\ 
  Katrina (2005) & 195 & 46 & 58 & 2,097 \\ 
  Danny (1997) & 82 & 147 & 54 & 2,113 \\ 
  Rita (2005) & 64 & 101 & 103 & 2,128 \\ 
  Gordon (2000) & 5 & 250 & 7 & 2,134 \\ 
  Arlene (2005) & 39 & 197 & 23 & 2,137 \\ 
  Dennis (1999) & 90 & 110 & 56 & 2,140 \\ 
  Ernesto (2006) & 124 & 68 & 63 & 2,141 \\ 
  Fran (1996) & 89 & 62 & 73 & 2,172 \\ 
  Bertha (1996) & 103 & 80 & 20 & 2,193 \\ 
   \bottomrule
\end{tabular}
\end{table}

### 2020-09-03 ehp_revision/tables/tornado_misclass.tex
Work some more on response

% latex table generated in R 4.0.2 by xtable 1.8-4 package
% Thu Sep  3 12:19:54 2020
\begin{table}[ht]
\centering
\caption{Caption. Limited to storms with at least 250 counties assessed as exposed based on at least one exposure metric considered in this study. Numbers are out of 2,396 counties in the study area (states in the eastern half of the US). Exposure assessment is based on the thresholds given in Table 1 of the main text. The Jaccard index shown in Figure [x] of the main text is based on numbers in the second through fourth columns (the value in the second column divide by the sum of numbers in the second through fourth columns). Storms are ordered based on the number of counties exposed to at least one of these two exposure metrics.} 
\begin{tabular}{cp{3cm}p{3cm}p{3cm}p{3cm}}
  \toprule
Storm & Exposed for both distance metric and flood metric & Exposed for distance metric but unexposed for flood metric & Exposed for flood metric but unexposed for distance metric & Unexposed for both distance metric and flood metric \\ 
  \midrule
Ivan (2004) & 79 & 205 & 238 & 1,874 \\ 
  Frances (2004) & 103 & 218 & 122 & 1,953 \\ 
  Dennis (2005) & 21 & 271 & 87 & 2,017 \\ 
  Jeanne (2004) & 80 & 217 & 77 & 2,022 \\ 
  Allison (2001) & 68 & 219 & 71 & 2,038 \\ 
  Cindy (2005) & 52 & 269 & 29 & 2,046 \\ 
  Ike (2008) & 48 & 185 & 101 & 2,062 \\ 
  Isidore (2002) & 30 & 238 & 64 & 2,064 \\ 
  Fay (2008) & 23 & 229 & 60 & 2,084 \\ 
  Bill (2003) & 39 & 191 & 65 & 2,101 \\ 
  Gustav (2008) & 36 & 198 & 57 & 2,105 \\ 
  Katrina (2005) & 47 & 194 & 47 & 2,108 \\ 
  Gordon (2000) & 7 & 248 & 19 & 2,122 \\ 
  Arlene (2005) & 11 & 225 & 29 & 2,131 \\ 
  Danny (1997) & 39 & 190 & 31 & 2,136 \\ 
  Floyd (1999) & 100 & 39 & 120 & 2,137 \\ 
  Fran (1996) & 46 & 105 & 77 & 2,168 \\ 
  Dennis (1999) & 38 & 162 & 19 & 2,177 \\ 
  Ernesto (2006) & 44 & 148 & 27 & 2,177 \\ 
  Bertha (1996) & 27 & 156 & 17 & 2,196 \\ 
  Rita (2005) & 4 & 161 & 26 & 2,205 \\ 
  Lee (2011) & 18 & 126 & 36 & 2,216 \\ 
   \bottomrule
\end{tabular}
\end{table}

>>>>

% latex table generated in R 4.0.2 by xtable 1.8-4 package
% Thu Sep  3 12:19:54 2020
\begin{table}[ht]
\centering
\caption{Caption. Limited to storms with at least 250 counties assessed as exposed based on at least one exposure metric considered in this study. Numbers are out of 2,396 counties in the study area (states in the eastern half of the US). Exposure assessment is based on the thresholds given in Table 1 of the main text. The Jaccard index shown in Figure [x] of the main text is based on numbers in the second through fourth columns (the value in the second column divide by the sum of numbers in the second through fourth columns). Storms are ordered based on the number of counties exposed to at least one of these two exposure metrics.} 
\begin{tabular}{cp{3cm}p{3cm}p{3cm}p{3cm}}
  \toprule
Storm & Exposed for both distance metric and tornado metric & Exposed for distance metric but unexposed for tornado metric & Exposed for tornado metric but unexposed for distance metric & Unexposed for both distance metric and tornado metric \\ 
  \midrule
Frances (2004) & 6 & 315 & 66 & 2,009 \\ 
  Ivan (2004) & 36 & 248 & 55 & 2,057 \\ 
  Cindy (2005) & 27 & 294 & 11 & 2,064 \\ 
  Jeanne (2004) & 13 & 284 & 22 & 2,077 \\ 
  Dennis (2005) & 0 & 292 & 6 & 2,098 \\ 
  Allison (2001) & 14 & 273 & 9 & 2,100 \\ 
  Katrina (2005) & 8 & 233 & 38 & 2,117 \\ 
  Fay (2008) & 15 & 237 & 26 & 2,118 \\ 
  Isidore (2002) & 1 & 267 & 6 & 2,122 \\ 
  Ike (2008) & 4 & 229 & 31 & 2,132 \\ 
  Gordon (2000) & 1 & 254 & 8 & 2,133 \\ 
  Gustav (2008) & 9 & 225 & 28 & 2,134 \\ 
  Bill (2003) & 4 & 226 & 22 & 2,144 \\ 
  Arlene (2005) & 2 & 234 & 7 & 2,153 \\ 
  Danny (1997) & 9 & 220 & 4 & 2,163 \\ 
  Rita (2005) & 8 & 157 & 41 & 2,190 \\ 
  Dennis (1999) & 0 & 200 & 1 & 2,195 \\ 
  Ernesto (2006) & 2 & 190 & 1 & 2,203 \\ 
  Bertha (1996) & 13 & 170 & 4 & 2,209 \\ 
  Fran (1996) & 1 & 150 & 4 & 2,241 \\ 
  Lee (2011) & 14 & 130 & 11 & 2,241 \\ 
  Floyd (1999) & 11 & 128 & 1 & 2,256 \\ 
   \bottomrule
\end{tabular}
\end{table}

### 2020-09-03 ehp_revision/tables/wind_misclass.tex
Work some more on response

% latex table generated in R 4.0.2 by xtable 1.8-4 package
% Tue Sep  1 17:11:57 2020
\begin{table}[ht]
\centering
\caption{Caption. Limited to storms with at least 200 counties assessed as exposed based on at least one exposure metric considered in this study. Numbers are out of 2,396 counties in the study area (states in the eastern half of the US). Exposure assessment is based on the thresholds given in Table 1 of the main text. The Jaccard index shown in Figure [x] of the main text is based on numbers in the second through fourth columns (the value in the second column divide by the sum of numbers in the second through fourth columns). Storms are ordered based on the number of counties exposed to at least one of these two exposure metrics.} 
\begin{tabular}{cp{3cm}p{3cm}p{3cm}p{3cm}}
  \toprule
Storm & Classified as exposed based on both distance metric and wind metric & Classified as exposed based on distance metric but unexposed by wind metric & Classified as exposed based on wind metric but unexposed by distance metric & Classified as unexposed based on both distance metric and wind metric \\ 
  \midrule
Frances-2004 &  44 & 277 &  13 & 2062 \\ 
  Cindy-2005 &  17 & 304 &   4 & 2071 \\ 
  Dennis-2005 &  18 & 274 &  26 & 2078 \\ 
  Ike-2008 & 166 &  67 &  82 & 2081 \\ 
  Ivan-2004 &  29 & 255 &  27 & 2085 \\ 
  Jeanne-2004 &  41 & 256 &   7 & 2092 \\ 
  Allison-2001 &  21 & 266 &   0 & 2109 \\ 
  Isidore-2002 &  29 & 239 &   7 & 2121 \\ 
  Katrina-2005 &  66 & 175 &  32 & 2123 \\ 
  Gordon-2000 &  11 & 244 &   6 & 2135 \\ 
  Fay-2008 &  54 & 198 &   7 & 2137 \\ 
  Gustav-2008 &  36 & 198 &  23 & 2139 \\ 
  Bertha-1996 & 179 &   4 &  62 & 2151 \\ 
  Danny-1997 &  45 & 184 &  12 & 2155 \\ 
  Arlene-2005 &   4 & 232 &   0 & 2160 \\ 
  Bill-2003 &  19 & 211 &   0 & 2166 \\ 
  Dennis-1999 &  17 & 183 &  13 & 2183 \\ 
  Hanna-2008 & 135 &  57 &  12 & 2192 \\ 
  Isabel-2003 & 105 &  42 &  56 & 2193 \\ 
  Ernesto-2006 &  93 &  99 &   4 & 2200 \\ 
  Helene-2000 &  18 & 174 &   0 & 2204 \\ 
  Rita-2005 &  26 & 139 &  20 & 2211 \\ 
  Fran-1996 &  46 & 105 &  30 & 2215 \\ 
  Earl-1998 & 133 &  36 &  11 & 2216 \\ 
  Floyd-1999 & 124 &  15 &  40 & 2217 \\ 
  Irene-2011 & 114 &   6 &  46 & 2230 \\ 
  Lee-2011 &  34 & 110 &   0 & 2252 \\ 
  Josephine-1996 &  62 &  61 &   3 & 2270 \\ 
  Hermine-2010 &  22 & 101 &   1 & 2272 \\ 
  Bonnie-2004 &   0 & 109 &   0 & 2287 \\ 
  Frances-1998 &  15 &  47 &   0 & 2334 \\ 
   \bottomrule
\end{tabular}
\end{table}

>>>>

% latex table generated in R 4.0.2 by xtable 1.8-4 package
% Thu Sep  3 12:19:54 2020
\begin{table}[ht]
\centering
\caption{Caption. Limited to storms with at least 250 counties assessed as exposed based on at least one exposure metric considered in this study. Numbers are out of 2,396 counties in the study area (states in the eastern half of the US). Exposure assessment is based on the thresholds given in Table 1 of the main text. The Jaccard index shown in Figure [x] of the main text is based on numbers in the second through fourth columns (the value in the second column divide by the sum of numbers in the second through fourth columns). Storms are ordered based on the number of counties exposed to at least one of these two exposure metrics.} 
\begin{tabular}{cp{3cm}p{3cm}p{3cm}p{3cm}}
  \toprule
Storm & Exposed for both distance metric and wind metric & Exposed for distance metric but unexposed for wind metric & Exposed for wind metric but unexposed for distance metric & Unexposed for both distance metric and wind metric \\ 
  \midrule
Frances (2004) & 44 & 277 & 13 & 2,062 \\ 
  Cindy (2005) & 17 & 304 & 4 & 2,071 \\ 
  Dennis (2005) & 18 & 274 & 26 & 2,078 \\ 
  Ike (2008) & 166 & 67 & 82 & 2,081 \\ 
  Ivan (2004) & 29 & 255 & 27 & 2,085 \\ 
  Jeanne (2004) & 41 & 256 & 7 & 2,092 \\ 
  Allison (2001) & 21 & 266 & 0 & 2,109 \\ 
  Isidore (2002) & 29 & 239 & 7 & 2,121 \\ 
  Katrina (2005) & 66 & 175 & 32 & 2,123 \\ 
  Gordon (2000) & 11 & 244 & 6 & 2,135 \\ 
  Fay (2008) & 54 & 198 & 7 & 2,137 \\ 
  Gustav (2008) & 36 & 198 & 23 & 2,139 \\ 
  Bertha (1996) & 179 & 4 & 62 & 2,151 \\ 
  Danny (1997) & 45 & 184 & 12 & 2,155 \\ 
  Arlene (2005) & 4 & 232 & 0 & 2,160 \\ 
  Bill (2003) & 19 & 211 & 0 & 2,166 \\ 
  Dennis (1999) & 17 & 183 & 13 & 2,183 \\ 
  Ernesto (2006) & 93 & 99 & 4 & 2,200 \\ 
  Rita (2005) & 26 & 139 & 20 & 2,211 \\ 
  Fran (1996) & 46 & 105 & 30 & 2,215 \\ 
  Floyd (1999) & 124 & 15 & 40 & 2,217 \\ 
  Lee (2011) & 34 & 110 & 0 & 2,252 \\ 
   \bottomrule
\end{tabular}
\end{table}

### 2020-09-03 ehp_revision/writing/ehp_discussion.tex
Work some more on response

Based on our results, the use of a distance-based metric to assess exposure to any of
these hazards, or the use of measurements from one hazard as a proxy for
exposure to any of the other hazards considered, would often introduce exposure
misclassification. This conclusion reinforces similar findings from a study of
Florida's 2004 storm season~\parencite{grabich2015measuring}.  For some
studies, such exposure misclassification might plausibly be differential.  For
example, tropical cyclone wind exposures tend to be concentrated in counties
near the coast, while tropical cyclone rain exposures sometimes extend well
inland.  If the etiologically-relevant exposure for a health outcome is extreme
rainfall but exposure is classified based on measurements of wind, the
probability of being misclassified as unexposed would be higher in inland
counties, while the probability of being misclassified as exposed would be
higher in coastal counties. If coastal counties differ from inland counties in
either the outcome of interest or in factors associated with risk of that
outcome, exposure misclassification would be
differential~\parencite{savitz2016interpreting}.  Such differential exposure
misclassification could bias estimates of tropical cyclone effects either
towards the null (estimating a lower or null association compared to the true
association that exists) or away from the null (estimating a larger association
than actually exists)~\parencite{savitz2016interpreting, armstrong1998effect}.

>>>>

Based on our results, the use of a distance-based metric to assess exposure to
any of these hazards, or the use of measurements from one hazard as a proxy for
exposure to any of the other hazards considered, would often introduce exposure
misclassification \textbf{(Tables S[x]--S[x])}. This conclusion reinforces
similar findings from a study of Florida's 2004 storm
season~\parencite{grabich2015measuring}.  For some studies, such exposure
misclassification might plausibly be differential.  For example, tropical
cyclone wind exposures tend to be concentrated in counties near the coast,
while tropical cyclone rain exposures sometimes extend well inland.  If the
etiologically-relevant exposure for a health outcome is extreme rainfall but
exposure is classified based on measurements of wind, the probability of being
misclassified as unexposed would be higher in inland counties, while the
probability of being misclassified as exposed would be higher in coastal
counties. If coastal counties differ from inland counties in either the outcome
of interest or in factors associated with risk of that outcome, exposure
misclassification would be differential~\parencite{savitz2016interpreting}.
Such differential exposure misclassification could bias estimates of tropical
cyclone effects either towards the null (estimating a lower or null association
compared to the true association that exists) or away from the null (estimating
a larger association than actually exists)~\parencite{savitz2016interpreting,
armstrong1998effect}.

### 2020-09-03 ehp_revision/writing/ehp_results.tex
Start some on response
Work some more on response

For peak sustained surface wind estimates, we found that the primary wind
exposure metric in the open-source data generally agreed well with the wind
radii reported in \ac{HURDAT2}. For most storms, $\>$90\% of counties were
assigned the same category of wind speed ($<$34~kt; 34\,--\,49.9~kt;
50\,--\,63.9~kt; $\ge$64~kt) by both data sources
(Figure~\ref{fig:windcomparison}).  Disagreement was limited to a few storms
(e.g., Hurricanes Sandy in 2012 and Ike in 2008). For these two storms, the
modeled wind speed in the open-source data somewhat overestimated the severity
of the storm's winds at landfall but then underestimated, particularly for
Hurricane Sandy, how far 34\,--\,49.9 kt winds extended from the storm's
central track further inland (Figure~S2). For epidemiology researchers who
would like to conduct sensitivity analysis using both sets of wind data,
we have included estimates from the \ac{HURDAT2} wind radii as a secondary
measure of county-level peak sustained wind in the open-source dataset
\parencite{hurricaneexposuredate}.

@@

We drew similar conclusions when we investigated all~46 tropical cyclones
between~1996 and~2011 (when data for all five metrics were available) for
which~100 or more counties were exposed based on at least one metric
(Figure~\ref{fig:jaccard}). In this figure, each row provides results for one
tropical cyclone, and each box in that row shows the Jaccard coefficient for a
pair of metrics. For all pairs of metrics, agreement in exposure assessment
was, at best, moderate for all but a few storms. When comparing distance- and
wind-based exposure assessment, only about 10\% of storms had Jaccard indices
higher than 0.6 (i.e., out of the counties assessed as exposed by at least one
of the two metrics in the pair,~60\si{\percent} or more were assessed the same
under both metrics). For comparisons of assessments based on other combinations
of distance-, wind-, rain-, and flood-based metrics, fewer than 5\% of storms
had Jaccard indices above 0.6.  The tornado-based metric had universally poor
agreement with other metrics in county-level classification across the tropical
cyclones considered.

>>>>

For peak sustained surface wind estimates, we found that the primary wind
exposure metric in the open-source data generally agreed well with the wind
radii reported in \ac{HURDAT2}. For most storms, $\>$90\% of counties were
assigned the same category of wind speed ($<$34~kt; 34\,--\,49.9~kt;
50\,--\,63.9~kt; $\ge$64~kt) by both data sources
(Figure~\ref{fig:windcomparison}).  Disagreement was limited to a few storms
(e.g., Hurricanes Sandy in 2012 and Ike in 2008). For these two storms, the
modeled wind speed in the open-source data somewhat overestimated the severity
of the storm's winds at landfall but then underestimated, particularly for
Hurricane Sandy, how far 34\,--\,49.9 kt winds extended from the storm's
central track further inland (Figure~S2). For epidemiology researchers who
would like to conduct sensitivity analysis using both sets of wind data,
we have included estimates from the \ac{HURDAT2} wind radii as a secondary
measure of county-level peak sustained wind in the open-source dataset
\parencite{hurricaneexposuredata}.

@@

We drew similar conclusions when we investigated all~46 tropical cyclones
between~1996 and~2011 (when data for all five metrics were available) for
which~100 or more counties were exposed based on at least one metric
(Figure~\ref{fig:jaccard}; \textbf{Tables S[x]--S[x] provide the underlying
numbers for the most extensive of these, the storms for which 250 of more
counties were exposed based on at least one metric}). In this figure, each row
provides results for one tropical cyclone, and each box in that row shows the
Jaccard coefficient for a pair of metrics. For all pairs of metrics, agreement
in exposure assessment was, at best, moderate for all but a few storms. When
comparing distance- and wind-based exposure assessment, only about 10\% of
storms had Jaccard indices higher than 0.6 (i.e., out of the counties assessed
as exposed by at least one of the two metrics in the pair,~60\si{\percent} or
more were assessed the same under both metrics). For comparisons of assessments
based on other combinations of distance-, wind-, rain-, and flood-based
metrics, fewer than 5\% of storms had Jaccard indices above 0.6.  The
tornado-based metric had universally poor agreement with other metrics in
county-level classification across the tropical cyclones considered.
